\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
%\chapter*{Zusammenfassung}
%\addcontentsline{toc}{chapter}{Zusammenfassung}



%In this master thesis I developed a novel hierarchical POMDP framework that performs reasoning on multiple spatial scales in order to lower computation times. The Multi-Scale POMDP solver is used in an object search and delivery task where the agent is given prior knowledge about the item locations in form of a belief distribution. 

In this master thesis we present a novel hierarchical POMDP framework to solve an object search and delivery task where the agent is given prior uncertain knowledge about the item locations. Object search and delivery problems are challenging as the agent has to perform reasoning with incomplete information.
%In this master thesis I studied an object search and delivery task where the agent is given prior knowledge about the item locations in form of a belief distribution.
This task is typically approached by next-best-view algorithms, POMDP high-level planners or with reinforcement learning. Next-best-view planners usually assume that the environment is unknown and thus do not consider prior knowledge. Solving POMDPs is computationally demanding and its application thus limited to small environments and reinforcement learning requires a lot of data which is time and labour intensive to collect. The proposed hierarchical POMDP framework peforms reasoning on multiple spatial scales in order to reduce computation time. 
%This thesis introduces a novel hierarchical POMDP framework that reasons on multiple spatial scales. 
The problem is first solved in the top layer of the hierarchy with a coarsely discretized state space. Its solution is refined in the lower layers with increasing resolution. Three different methods to combine the spatial scales are discussed and validated in simulation. We show that a two layer multi-scale POMDP decreases computation time by one order of magnitude allowing for real-time applications while maintaining high solution quality. For large problems that require three layers to reach the desired resolution, computation time speedups by two orders of magnitude are achieved.
